### 2023-03-31 reachable-resilience.tex
up

%
\iffalse
%
\textcolor{blue}{
et encore: renforcer sur l'hypothèses sur I, J tous les deux clos par le haut+bas.
}
%
\textcolor{blue}{
compute the sets of $(I,J,k)$ st S is resilient.\\
max des I,J possibles \\
}
%
\fi

@@

@@

The computability of $\uparrow \post^*(s)$ seems a strong hypothesis. What are the WSTS for which $\uparrow \post^*(s)$ is computable for $s \in S$ ?
Ozkan \cite{DBLP:conf/gg/Ozkan22} argues that it is the WSTS for which the following problem is decidable.

@@

@@

Unfortunately, reachable-resilience is undecidable for (general) WSTS even with strong monotony.
This stems from the fact that $t$-liveness is undecidable for reset Petri-Nets.

Since $t$-liveness is undecidable for reset Petri-Nets that are WSTS with strong monotony, from Proposition \ref{reductions},  we deduce that reachable-resilience is undecidable for WSTS with strong monotony.

\begin{theorem}
{\sc reachable-resilience} is undecidable for WSTS with strong monotony.
\end{theorem}

\begin{proposition}
In WSTS with strong monotony, the bounded reachable-resilience problem is
reducible to the $k$-reachable-resilience problem.
\end{proposition}

\begin{proof}
strong WSTS
$\pred^*(I) = \pred^{k}(I)$
Check all $k$ until $\pred^*(I) = \pred^{k}(I)$.
\end{proof}

>>>>

@@

As in the Section~3, we study decidability results for different pairs of sets $\Safe$ and $\Bad$ downard closed and upward closed.

@@

The computability of $\uparrow \post^*(s)$ seems a strong hypothesis. What are the WSTS for which $\uparrow \post^*(s)$ is computable for $s \in S$ ?
Ozkan \cite{DBLP:conf/gg/Ozkan22} argues that it is precisely the WSTS for which the following problem is decidable.

@@

Unfortunately, state-resilience is undecidable for (general) WSTS even with strong monotony.
This stems from the fact that $t$-liveness is undecidable for reset Petri-Nets.

Since $t$-liveness is undecidable for reset Petri-Nets that are WSTS with strong monotony, from Proposition \ref{reductions},  we deduce that state-resilience is undecidable for WSTS with strong monotony.

\begin{theorem}
{\sc State-resilience} is undecidable for WSTS with strong monotony.
\end{theorem}

\begin{proposition}
In WSTS with strong compatibility and effective pred-basis, the bounded state-resilience problem is
reducible to the $k$-state-resilience problem.
\end{proposition}

\begin{proof}
% strong WSTS
% $\pred^*(I) = \pred^{k}(I)$
% Check all $k$ until $\pred^*(I) = \pred^{k}(I)$.
Since $\Safe=\uparrow \Safe$ and
$\mathscr{S}=(S,\rightarrow,\leq)$ is a WTSTS with strong %upward-
compatibility, then $\pred^n(\Safe)= \uparrow~\pred^n(\Safe)$ for all $n \in \N$,
and there exists $n_0 \in \N$ such that 
$\pred^{n_0}(\Safe) = \uparrow \pred^{n_0}(\Safe) = \uparrow \pred^*(\Safe) = \pred^*(\Safe)$.
We
\end{proof}

@@
